Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-11 draft/accordionComplexSurfaces.tex
Proposition flip of accordions.

\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=1]{kissings}}
	\caption{Two representations of a pair of kissing walks.}
	\label{fig:kissings}
\end{figure}
The left hand side of the picture is as in \fref{fig:kissing}, and the right hand side is simply a different representation of it.
On the surface~$\surface_{\bar Q}$, the dual dissections~$\dissection$ and~$\dissection\dual$ are as on \fref{fig:kissingVSCrossing} (right).

@@

For a vertex~$v \in V$ on the boundary of~$\surface$, we denote by~$\vprevious{v}$ (resp.~$\vnext{v}$) the blossom vertex previous (resp.~next) to~$v$ on the counterclockwise order around the boundary of~$\surface$.
For an edge~$a$ of~$\dissection$, we denote by~$\vprevious{a}$ (resp.~$\vnext{a}$) the curve obtained by moving each endpoint~$v$ of~$a$ as follows:
\begin{itemize}
\item if~$v$ is on the boundary of~$\surface$, then move (continuously) $v$ along the boundary of~$\surface$ until it reaches~$\vprevious{v}$ (resp.~$\vnext{v}$),
\item if~$v$ is a puncture, then rotate around~$v$ in counterclockwise direction (resp.~clockwise direction).
\end{itemize}
Examples are illustrated in \fref{fig:peakDeep}.
%
\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=.7]{peakDeep}}
	\caption{The curves~$\vprevious{a}$ (left) and $\vnext{a}$ (right) associated to an edge~$a$ of~$\dissection$ for three different dissections.}
	\label{fig:peakDeep}
\end{figure}

@@

\begin{proposition}
\label{prop:flip}
Let~$F$ be a non-kissing facet in~$\NKC$ and let~$\omega \in F$ be a bending walk.
Let~$\alpha$ and~$\beta$ be the distinguished arrows of~$\omega$ (see Proposition \ref{prop:numberOfDistinguishedArrows}), and~$\sigma$ be the distinguished substring of~$\omega$, which splits~$\omega$ into~$\omega = \rho \sigma \tau$.
Let~$\alpha'$ and~$\beta'$ be the other two arrows of~$Q_1\blossom$ incident to the endpoints of~$\sigma$ and such that~$\alpha'\alpha \in I$ or~$\alpha\alpha' \in I$, and $\beta'\beta \in I$ or~$\beta\beta' \in I$.
Let~$\mu \eqdef \distinguishedWalk{\alpha'}{F \ssm \{\omega\}}$ and~$\nu \eqdef \distinguishedWalk{\beta'}{F \ssm \{\omega\}}$ be the distinguished walks of~$F \ssm \{\omega\}$ at~$\alpha'$ and~$\beta'$ respectively.
Then
\begin{enumerate}[(i)]
\item The walk~$\mu$ splits into~$\mu = \rho' \sigma \tau$ and the walk~$\nu$ splits into~$\nu = \rho \sigma \tau'$.
\item The walk~$\omega' \eqdef \rho' \sigma \tau'$ is kissing~$\omega$ but no other~walk~of~$F$. Moreover, $\omega'$ is the only other (undirected) walk besides~$\omega$ which is not kissing any other walk of~$F \ssm \{\omega\}$.
\end{enumerate}
\end{proposition}

@@

@@

\begin{example}
\label{exm:gcdVectorsWalks}
For instance, the $\b{g}$-, $\b{c}$-, and $\b{d}$-matrices of the facet illustrated in \fref{} are given by
\[
\gvectors{F} = 
\begin{blockarray}{ccc}
	{\color{blue} \bullet} & {\color{purple} \bullet} & \\[-.1cm]
	\begin{block}{[cc]c}
	1 & 0 & \!\!\!\circled{1} \\
	-1\!\! & \!\!-1 & \!\!\!\circled{2} \\
	\end{block}
\end{blockarray}
\qquad\qquad
\cvectors{F} = 
\begin{blockarray}{ccc}
	{\color{blue} \bullet} & {\color{purple} \bullet} & \\[-.1cm]
	\begin{block}{[cc]c}
	1 & \!\!-1 & \!\!\!\circled{1} \\
	0 & \!\!-1 & \!\!\!\circled{2} \\
	\end{block}
\end{blockarray}
\qquad\qquad
\dvectors{F} = 
\begin{blockarray}{ccc}
	{\color{blue} \bullet} & {\color{purple} \bullet} & \\[-.1cm]
	\begin{block}{[cc]c}
	1 & 0 & \!\!\!\circled{1} \\
	0 & 0 & \!\!\!\circled{2} \\
	\end{block}
\end{blockarray}
\]
(\ie columns are the $\b{g}$-, $\b{c}$-, $\b{d}$-vectors of the elements of the facet).

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.7]{gcdVectors}}
	\caption{A non-kissing facet (left), an accordion facet (middle) and a slalom facet (right) that correspond via the bijections of Theorem~\ref{thm:complexesCoincide} and Proposition~\ref{prop:accordionsSlaloms}. The~$\b{g}$-, $\b{c}$-, and $\b{d}$-matrices of this facet are given in Example~\ref{exm:gcdVectorsWalks}.}
	\label{fig:gcdVectors}
\end{figure}
\end{example}

>>>>

\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=1]{kissings}}
	\caption{Two representations of a pair of kissing walks.}
	\label{fig:kissings}
\end{figure}
The left hand side of the picture is as in \fref{fig:kissing}, and the right hand side is simply a different representation of it.
On the surface~$\surface_{\bar Q}$, the dual dissections~$\dissection$ and~$\dissection\dual$ are as on \fref{fig:kissingVSCrossing} (on the right hand side).

@@

For a vertex~$v \in V$ on the boundary of~$\surface$, we denote by~$\vprevious{v}$ (resp.~$\vnext{v}$) the blossom vertex previous (resp.~next) to~$v$ on the clockwise order around the boundary of~$\surface$.
For an edge~$a$ of~$\dissection$, we denote by~$\vprevious{a}$ (resp.~$\vnext{a}$) the curve obtained by moving each endpoint~$v$ of~$a$ as follows:
\begin{itemize}
\item if~$v$ is on the boundary of~$\surface$, then move (continuously) $v$ along the boundary of~$\surface$ until it reaches~$\vprevious{v}$ (resp.~$\vnext{v}$),
\item if~$v$ is a puncture, then rotate around~$v$ in counterclockwise direction (resp.~clockwise direction).
\end{itemize}
Examples are illustrated in \fref{fig:peakDeep}.
%
\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=.7]{peakDeep}}
	\caption{The curves~$\vprevious{a}$ (left) and $\vnext{a}$ (right) associated to an edge~$a$ of~$\dissection$ for three different dissections.}
	\label{fig:peakDeep}
\end{figure}

@@

\begin{proposition}
\label{prop:flip}
Let~$F$ be a non-kissing facet in~$\NKC$ and let~$\omega \in F$ be a bending walk.
Let~$\alpha$ and~$\beta$ be the distinguished arrows of~$\omega$ (see Proposition \ref{prop:numberOfDistinguishedArrows}), and~$\sigma$ be the distinguished substring of~$\omega$, which splits~$\omega$ into~$\omega = \rho \sigma \tau$.
Let~$\alpha'$ and~$\beta'$ be the other two arrows of~$Q_1\blossom$ incident to the endpoints of~$\sigma$ and such that~$\alpha'\alpha \in I$ or~$\alpha\alpha' \in I$, and $\beta'\beta \in I$ or~$\beta\beta' \in I$.
Let~$\mu \eqdef \distinguishedWalk{\alpha'}{F \ssm \{\omega\}}$ and~$\nu \eqdef \distinguishedWalk{\beta'}{F \ssm \{\omega\}}$ be the distinguished walks of~$F \ssm \{\omega\}$ at~$\alpha'$ and~$\beta'$ respectively.
Then
\begin{enumerate}[(i)]
\item The walk~$\mu$ splits into~$\mu = \rho' \sigma \tau$ and the walk~$\nu$ splits into~$\nu = \rho \sigma \tau'$.
\item The walk~$\omega' \eqdef \rho' \sigma \tau'$ is kissing~$\omega$ but no other~walk~of~$F$. Moreover, $\omega'$ is the only other (undirected) walk besides~$\omega$ which is not kissing any other walk of~$F \ssm \{\omega\}$.
\end{enumerate}
\end{proposition}
The walk~$\omega'$ of Proposition \ref{prop:flip} is the \defn{flip} of \defn{mutation} of~$F$ at~$\omega$.

@@

The mutation of non-kissing facets translates on~$\surface(\bar Q)$ as follows.

\begin{proposition}
\label{prop:mutationAccordions}
Let~$F$ be a facet of the non-crossing complex~$\NCC$, and let~$\gamma \in F$.
Then~$F$ forms a~$B$-dissection of the surface, and~$\gamma$ lies in at least one of the two configutations~$\ZZZ$ and~$\SSS$ with the other curves of the dissection (where the endpoints may be punctures). 
\begin{itemize}
 \item 
\end{itemize}

\end{proposition}

@@

\begin{example}
\label{exm:gcdVectorsWalks}
For instance, the $\b{g}$-, $\b{c}$-, and $\b{d}$-matrices of the facet illustrated in \fref{} are given by
\[
\gvectors{F} = 
\begin{blockarray}{ccc}
	{\color{blue} \bullet} & {\color{purple} \bullet} & \\[-.1cm]
	\begin{block}{[cc]c}
	1 & 0 & \!\!\!\circled{1} \\
	-1\!\! & \!\!-1 & \!\!\!\circled{2} \\
	\end{block}
\end{blockarray}
\qquad\qquad
\cvectors{F} = 
\begin{blockarray}{ccc}
	{\color{blue} \bullet} & {\color{purple} \bullet} & \\[-.1cm]
	\begin{block}{[cc]c}
	1 & \!\!-1 & \!\!\!\circled{1} \\
	0 & \!\!-1 & \!\!\!\circled{2} \\
	\end{block}
\end{blockarray}
\qquad\qquad
\dvectors{F} = 
\begin{blockarray}{ccc}
	{\color{blue} \bullet} & {\color{purple} \bullet} & \\[-.1cm]
	\begin{block}{[cc]c}
	0 & 1 & \!\!\!\circled{1} \\
	1 & 1 & \!\!\!\circled{2} \\
	\end{block}
\end{blockarray}
\]
(\ie columns are the $\b{g}$-, $\b{c}$-, $\b{d}$-vectors of the elements of the facet).

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.7]{gcdVectors}}
	\caption{A non-kissing facet (left), an accordion facet (middle) and a slalom facet (right) that correspond via the bijections of Theorem~\ref{thm:complexesCoincide} and Proposition~\ref{prop:accordionsSlaloms}. Their~$\b{g}$-, $\b{c}$-, and $\b{d}$-matrices of this facet are given in Example~\ref{exm:gcdVectorsWalks}.}
	\label{fig:gcdVectors}
\end{figure}
\end{example}
